### 2018-08-09 paper/approach.tex
Replaces Sphinx~\cite{Sphinx} with \ac{Sphinx}

After the initial, out-of-band setup, file transfer happens along
onion routes with the following features:\\
\textbf{Stateless.} There is no mandatory circuit creation, the file transfer can be
  done in a stateless way. \\
 \textbf{Predictive.} The choice of which nodes is placed in which onion routing
  layer is informed on a predictive model for availability, disseminated
  by an overlay and queried by random peer sampling (RPS). Note that availability predictions only influence how nodes returned by the random peer sampling service are distributed among layers, but have no impact on the overall population of nodes making up the onion route. This population is controlled by the random peer sampling service, which we assume is secure. This is important to ensure strong privacy protection, and we return to this point in the Security Discussion of Section~\ref{security-discussion}.\\
 \textbf{Probabilistic.} Instead of source routes with one node per onion layer, each
  layer consists of a set of nodes and although the source route still
  determines the sequence of layers, the actual node used for the next
  hop of forwarding is selected from the set in an ad-hoc way,
  resulting in a source-bounded random walk.\\
 \textbf{Onion Routing.} Put simply, in onion routing, the sender creates
  a source route and encapsulates the payload and next-hop information in layers (by
  encryption), that are \emph{peeled} (decrypted) one by one along the
  route. By virtue of these layers, the forwarding nodes on the
  route do not know where on the route they are and thus whether they
  have received a packet directly from the sender or some other
  intermediate node. We base our format for layering and peeling on the
  Sphinx~\cite{Sphinx} mix-header format, which we extend to allow for the
  changes above, described in \cref{Sphinxes}.

% \begin{description}
% \item [Stateless.] There is no mandatory circuit creation, the file transfer can be
%   done in a stateless way. 
% \item [Predictive.] The choice of nodes included in the onion routing
%   layers is based on a predictive model for availability, disseminated
%   by an overlay and queried by random peer sampling.
% \item [Probabilistic.] Instead of source routes with one node per onion layer, each
%   layer consists of a set of nodes and although the source route still
%   determines the sequence of layers, the actual node used for the next
%   hop of forwarding is selected from the set in an ad-hoc way,
%   resulting in a source-bounded random walk.
% \item[Onion Routing.] Put simply, in onion routing, the sender creates
%   a source route and 
%   encapsulates the payload and next-hop information in layers (by
%   encryption), that are \emph{peeled} (decrypted) one by one along the
%   route. By virtue of these layers, the forwarding nodes on the
%   route do not know where on the route they are and thus whether they
%   have received a packet directly from the sender or some other
%   intermediate node. We base our format for layering and peeling on
%   Sphinx~\cite{Sphinx}, with some modification to allow for the
%   changes above, described in \cref{Sphinxes}.
% \end{description}

@@

As depicted in Figure~\ref{fig:outline}, \ac{SPORES} relies on a predictive and probabilistic onion routing protocol (\ac{SPOR}). \ac{SPOR} in turn combines a multi-set mix-header format (\Sphinxes) together with a node selection protocol that exploits decentralized prediction regarding node availability to optimize the reliability of \Sphinxes without jeopardizing its security properties.
%% Particularly, \sphinxes (\cref{Sphinxes}), is an adaptation of the 
%% \sonja{do we apply all categories here?} Sphinx~\cite{Sphinx} mix-header format.
%% This means that we inherit some properties from Sphinx and due to being only a 
%% header format, it only imposes some restrictions in the above categories.
\Sphinxes (Figure~\ref{fig:outline} \ding{202}) provides, just as Sphinx, unidirectional (network structure), 
message-based (performance) communication.
But unlike Sphinx, \Sphinxes is an hybrid source-hop-by-hop routed, and a
source-bounded random walk (communication 
model). \Sphinxes relies on a flat routing-topology (network structure) with fair 
scheduling (communication model) --- as all packets are indistinguishable they 
must be processed on a first-in-first-out basis.
\Sphinxes also introduces some probability to the node selection, but this is 
only a probabilistic selection among already selected nodes and only 
interesting against passive adversaries (an active adversary can learn the 
entire set just as she can learn the single node constituting a layer of a
secure onion-routing scheme without endangering the security
properties~\cite{CLOnionRouting}).

>>>>

After the initial, out-of-band setup, file transfer happens along
onion routes with the following features:\\
\textbf{Stateless.} There is no mandatory circuit creation, the file transfer can be
  done in a stateless way. \\
 \textbf{Predictive.} The choice of which nodes is placed in which onion routing
  layer is informed on a predictive model for availability, disseminated
  by an overlay and queried by random peer sampling (RPS). Note that availability predictions only influence how nodes returned by the random peer sampling service are distributed among layers, but have no impact on the overall population of nodes making up the onion route. This population is controlled by the random peer sampling service, which we assume is secure. This is important to ensure strong privacy protection, and we return to this point in the Security Discussion of Section~\ref{security-discussion}.\\
 \textbf{Probabilistic.} Instead of source routes with one node per onion layer, each
  layer consists of a set of nodes and although the source route still
  determines the sequence of layers, the actual node used for the next
  hop of forwarding is selected from the set in an ad-hoc way,
  resulting in a source-bounded random walk.\\
 \textbf{Onion Routing.} Put simply, in onion routing, the sender creates
  a source route and encapsulates the payload and next-hop information in layers (by
  encryption), that are \emph{peeled} (decrypted) one by one along the
  route. By virtue of these layers, the forwarding nodes on the
  route do not know where on the route they are and thus whether they
  have received a packet directly from the sender or some other
  intermediate node. We base our format for layering and peeling on the
  \ac{Sphinx} mix-header format, which we extend to allow for the
  changes above, described in \cref{Sphinxes}.

% \begin{description}
% \item [Stateless.] There is no mandatory circuit creation, the file transfer can be
%   done in a stateless way. 
% \item [Predictive.] The choice of nodes included in the onion routing
%   layers is based on a predictive model for availability, disseminated
%   by an overlay and queried by random peer sampling.
% \item [Probabilistic.] Instead of source routes with one node per onion layer, each
%   layer consists of a set of nodes and although the source route still
%   determines the sequence of layers, the actual node used for the next
%   hop of forwarding is selected from the set in an ad-hoc way,
%   resulting in a source-bounded random walk.
% \item[Onion Routing.] Put simply, in onion routing, the sender creates
%   a source route and 
%   encapsulates the payload and next-hop information in layers (by
%   encryption), that are \emph{peeled} (decrypted) one by one along the
%   route. By virtue of these layers, the forwarding nodes on the
%   route do not know where on the route they are and thus whether they
%   have received a packet directly from the sender or some other
%   intermediate node. We base our format for layering and peeling on
%   \ac{Sphinx}, with some modification to allow for the
%   changes above, described in \cref{Sphinxes}.
% \end{description}

@@

As depicted in Figure~\ref{fig:outline}, \ac{SPORES} relies on a predictive and probabilistic onion routing protocol (\ac{SPOR}). \ac{SPOR} in turn combines a multi-set mix-header format (\Sphinxes) together with a node selection protocol that exploits decentralized prediction regarding node availability to optimize the reliability of \Sphinxes without jeopardizing its security properties.
%% Particularly, \sphinxes (\cref{Sphinxes}), is an adaptation of the 
%% \sonja{do we apply all categories here?} \ac{Sphinx} mix-header format.
%% This means that we inherit some properties from Sphinx and due to being only a 
%% header format, it only imposes some restrictions in the above categories.
\Sphinxes (Figure~\ref{fig:outline} \ding{202}) provides, just as Sphinx, unidirectional (network structure), 
message-based (performance) communication.
But unlike Sphinx, \Sphinxes is an hybrid source-hop-by-hop routed, and a
source-bounded random walk (communication 
model). \Sphinxes relies on a flat routing-topology (network structure) with fair 
scheduling (communication model) --- as all packets are indistinguishable they 
must be processed on a first-in-first-out basis.
\Sphinxes also introduces some probability to the node selection, but this is 
only a probabilistic selection among already selected nodes and only 
interesting against passive adversaries (an active adversary can learn the 
entire set just as she can learn the single node constituting a layer of a
secure onion-routing scheme without endangering the security
properties~\cite{CLOnionRouting}).

### 2018-08-09 paper/sphinxes.tex
fixed sphinx public key denotation
up
s/p2p-private-cloud/spores/g to replace remaining ones
Replaces Sphinx~\cite{Sphinx} with \ac{Sphinx}

%!TEX root = p2p-private-cloud.tex

@@

Finally, \(\alpha_1\) is blinded into \(\alpha_2\) with a key derived from 
\(s_1\).
Then the triple \((\alpha_2, \beta_2, \gamma_2)\) is sent to the node with 
address \(d_2\).

When node \(n\) discovers \(d_{n+1} = *\) it knows that the message is intended 
for itself and thus stops the forwarding.

@@

In Sphinx we denoted the public key for layer \(i\) as \(\pk_i\).
Since we have \(m\) alternative nodes with different keys, let us denote them 
by \(\pk_i^{(1)}, \dotsc, \pk_i^{(m)}\).

@@

We will synchronize our detailed descriptions with that of 
Sphinx~\cite{Sphinx}, hence we will use the following notation:
\begin{itemize}
  \item \(\kappa\) is the security parameter.
    The adversary must thus do about \(2^\kappa\) work to break the security.

>>>>

%!TEX root = spores.tex

@@

Finally, \(\alpha_1\) is blinded into \(\alpha_2\) with a key derived from 
\(s_1\).
Then the triple \((\alpha_2, \beta_2, \gamma_2)\) is sent to the node with 
address \(d_2\). When node \(n\) discovers \(d_{n+1} = *\) it knows that the message is intended 
for itself and thus stops the forwarding.

@@

In Sphinx, the public key for layer \(i\) is denoted as \(\pk_i\).
Since we have \(m\) alternative nodes with different keys, let us denote them 
by \(\pk_i^{(1)}, \dotsc, \pk_i^{(m)}\).

@@

We will synchronize our detailed descriptions with that of 
\ac{Sphinx}, hence we will use the following notation:
\begin{itemize}
  \item \(\kappa\) is the security parameter.
    The adversary must thus do about \(2^\kappa\) work to break the security.
